### 2013-02-24 doc/sosp13/overview.tex
sosp repo. put in sosp submission guidelines. new title

\paragraph{Exploiting Latency Tolerance} As we will show later, Grappa can tolerate latencies way beyond that of the network. Therefore, Grappa can afford to \emph{trade latency for throughput}: by {\em increasing} latency in key components of the system we are able to increase our aggregate random access bandwidth (by delaying and aggregating messages), our synchronization bandwidth (by delegating operations to remote nodes), and our ability to improve load imbalance (work stealing increases latency).

>>>>

% \paragraph{Exploiting Latency Tolerance} As we will show later, Grappa can tolerate latencies way beyond that of the network. Therefore, Grappa can afford to \emph{trade latency for throughput}: by {\em increasing} latency in key components of the system we are able to increase our aggregate random access bandwidth (by delaying and aggregating messages), our synchronization bandwidth (by delegating operations to remote nodes), and our ability to improve load imbalance (work stealing increases latency).

### 2013-02-24 doc/sosp13/relatedwork.tex
sosp repo. put in sosp submission guidelines. new title

\paragraph{Comparable frameworks} Distributed graph processing
frameworks like Pregel~\cite{pregel:2010} and Distributed
GraphLab~\cite{distgraphlab:vldb12} share similar goals as
Grappa. Pregel adopts a bulk-synchronous parallel (BSP) execution
model, which makes it inefficient on workloads that could prioritize
vertices. GraphLab, on the other hand, schedules vertex computations
individually, allowing prioritization, which gives faster convergence
in a variety of iterative algorithms.  GraphLab, however, imposes a
rigid computation model where programmers must express computation as
transformations on a vertex and its edge list only, with only
information from adjacent vertexes. Pregel is only slightly less
restrictive, as the input data can be any vertex in the graph.  Grappa
also supports dynamic parallelism with asynchronous execution, but
parallelism is expressed as tasks or loop iterations, which is a far
more general programming model for irregular computation tasks.

>>>>

\paragraph{Comparable frameworks} Distributed graph processing
frameworks like Pregel~\cite{pregel:2010} and Distributed
GraphLab~\cite{distgraphlab:vldb12} share similar goals as
Grappa. Pregel adopts a bulk-synchronous parallel (BSP) execution
model, which makes it inefficient on workloads that could prioritize
vertices. GraphLab, on the other hand, schedules vertex computations
individually, allowing prioritization, which gives faster convergence
in a variety of iterative algorithms.  GraphLab, however, imposes a
rigid computation model where programmers must express computation as
transformations on a vertex and its edge list only, with information only
from adjacent vertexes. Pregel is only slightly less
restrictive, as the input data can be any vertex in the graph.  Grappa
also supports dynamic parallelism with asynchronous execution, but
parallelism is expressed as tasks or loop iterations, which is a far
more general programming model for irregular computation tasks.

### 2013-02-24 doc/sosp13/tasks.tex
sosp repo. put in sosp submission guidelines. new title

\paragraph{Work stealing} 
When the scheduler finds no work to assign to its workers, it
commences to steal work from other cores using an asynchronous
\texttt{call\_on} active message.  It chooses a victim at random until it
finds one with a non-zero amount of work in its public task queue.  The scheduler steals half of the tasks it finds at the victim.

>>>>

\paragraph{Work stealing} 
When the scheduler finds no work to assign to its workers, it
commences to steal work from other cores using an asynchronous
\texttt{call\_on} active message.  It chooses a victim at random until it
finds one with a non-zero amount of work in its public task queue.  The scheduler steals half of the tasks it finds at the victim.
Work stealing is particularly interesting in Grappa since performance depends
on having many active worker threads on each core. Even if there are many
active threads, if they are all suspended on long-latency operations,
then the core is underutilized. We choose to initiate one outstanding
steal whenever the ready queue is empty there are idle worker threads.
